Synthesis of Network Intrusion Detection Rules

### 2019-10-17 paper/paper.tex
pass up to section 2.1

\Mar{Lucas/Guilherme, verifique se isto esta correto}
Figure~\ref{fig:synflood-example} shows an example rule of
Suricata~\cite{suricata}, a popular open-source \nids{} maintained by
the Open Information Security Foundation (OISF)~\cite{oisf}. A
Suricata rule is divided in three parts---action, header, and rule
options~\cite{suri-rule-format}. The action part appears as the first
word in the rule description. In this case, \CodeIn{alert}. An action
denotes the task that needs to be executed if the rule pattern is
satisfied. In this case, a message will be sent to sys admins if the
rule pattern is satisfied. Other actions include pass, drop, and
reject. The header comes after the action in the rule description. It
restricts the information flow covered by the rule. For this rule, the
header is \CodeIn{tcp \$HOME\_NET any -> \$EXTERNAL\_NET any}, which
instructs Suricata to inspect \CodeIn{tcp} traffic flowing from any
port in the home network to any other address outside the home
network. The variables \CodeIn{\$HOME\_NET} and
\CodeIn{\$EXTERNAL\_NET} are configurable. The rule options come after
the header. It is a semi-colon-separated sequence of options, where
each property is a key-value pair describing a distinct characteristic
of the attack.

>>>>

Figure~\ref{fig:synflood-example} shows an example rule of
Suricata~\cite{suricata}, a popular open-source \nids{} maintained by
the Open Information Security Foundation (OISF)~\cite{oisf}. A
Suricata rule is divided in three parts---action, header, and rule
options~\cite{suri-rule-format}. The action part appears as the first
word in the rule description. An action denotes the task that needs to
be executed if the rule pattern is satisfied. In this example, a
message will be sent to system administrators if the rule pattern is
satisfied. The header comes after the action in the rule
description. It restricts the information flow covered by the
rule. For this rule, the header is \CodeIn{tcp \$HOME\_NET any ->
  \$EXTERNAL\_NET any}. It instructs Suricata to inspect \CodeIn{tcp}
traffic flowing from any port in the home network to any other address
outside the home network. The variables \CodeIn{\$HOME\_NET} and
\CodeIn{\$EXTERNAL\_NET} are configurable. The rule options come after
the header. It is a semi-colon-separated sequence of key-value
pairs. Some options serve to document the analyzed traffic (\eg{},
``msg'', ``classtype'', and ``sid'') whereas the remaining properties
describe characteristics of the attack (\eg, ``flags'', ``threshold'',
and ``content''). The main challenge in synthesizing rules is to
discover the set of options that make a rule to capture the malicious
traffic, but ignore the benign traffic.
